Vertical and oblique transmission fluctuating in time and in space

### 2018-06-20 ms/ms_sunnyvale.tex
MWF changes to results summary in discussion

Comparing our results with previous results from a similar model with a fixed rate~\citep{Ram2018}, we find that a protected polymorphism can be maintained only if fluctuations in the rate of vertical transmission are small, and that stronger selection permits larger fluctuations while still maintaining a protected polymorphism. 
In the case of fluctuations in space, the greater the separation between the two populations, the larger the fluctuations can be while still maintaining polymorphism; however, as migration becomes more frequent, even small differences in the vertical transmission rate will eliminate the polymorphism.
When fluctuations are stochastic, we find that if vertical transmission covaries with selection, the phenotype that is more likely to be vertically transmitted specifically when it is favored will likely fix in the population, eventually.
However, if transmission and selection are independent, then a polymorphism can be maintained if selection doesn't, on average, favor one phenotype over the other.

>>>>

Comparing our results with previous results from a similar model with a fixed rate of vertical transmission~\citep{Ram2018}, we find that a protected polymorphism can be maintained only if fluctuations in the rate of vertical transmission are small, and that stronger selection on the transmitted trait permits larger fluctuations in the rate of transmission while still maintaining a protected polymorphism. 
In the case of fluctuations in space, the greater the separation between the two populations, the larger the fluctuations can be while still maintaining polymorphism; however, as migration becomes more frequent, even small differences in the vertical transmission rate will eliminate the polymorphism.
When fluctuations are stochastic, we find that if vertical transmission covaries with selection, the phenotype that has a higher probability of being vertically transmitted  when it is favored will likely eventually fix in the population.
However, if transmission and selection are independent, then a polymorphism can be maintained if selection does not, on average, favor one phenotype over the other.
